NGO analysis

### 2022-07-28 Dashboard/NGO Analysis dashboard alpha v002.Rmd
Stylering.

  ## OPX KPI--------------------------------------------------------------------
  # Creating OPX KPI
  KPI_OPX_num <- reactive({
    # testing for data quality, returning NA if bad
    if (datatest() == TRUE) {
      NA
    } else {
      exceldata() |>
        # most recent year
        filter(year == max(year)) |>
        # Calculating the value as a %
        transmute(
          KPI_OPX =
            sum(revenue_private_contributions,
                revenue_investments, assets_cash_in_bank_and_cash_equivalents,
                na.rm = TRUE) /
              sum(liability_short_term_grants_payable,
                  liability_revocable_endowments,
                  liability_long_term_grants_payable, na.rm = TRUE) * 100
        ) |>
        # Just the single number
        pull() |>
        first()
    }
  })

@@

```{r reactive_plots, include=FALSE}

# Beginning of the second reactive chunk =======================================
# It's necessary to split the observers into separate parts, with all necessary
# code duplicated, because of R's limitations.

@@

    # Testing and creating data frame
    html_test_create(input$html$datapath,
                 as.character(input$start), as.character(input$end))
  })

@@

  ## Excel data test (also above)-----------------------------------------------
  # Reactive function to test for Excel data quality (basic)
  datatest <- reactive({
    # let me know if anyone has a better idea for testing
    if (mean(unlist(lapply(exceldata(), is.character))) != 0) {
      TRUE
    } else {
      FALSE
    }
  })
  # Let the magic/disaster happen (i.e. execute when the user clicks the button)
}) |> bindEvent(input$click)

```

>>>>

  ## OPX KPI--------------------------------------------------------------------
  # Creating OPX KPI
  KPI_OPX_num <- reactive({
    # testing for data quality, returning NA if bad
    if (datatest() == TRUE) {
      NA
    } else {
      exceldata() |>
        # most recent year
        filter(year == max(year)) |>
        # Calculating the value as a %
        transmute(
          KPI_OPX =
            sum(revenue_private_contributions,
              revenue_investments, assets_cash_in_bank_and_cash_equivalents,
              na.rm = TRUE
            ) /
              sum(liability_short_term_grants_payable,
                liability_revocable_endowments,
                liability_long_term_grants_payable,
                na.rm = TRUE
              ) * 100
        ) |>
        # Just the single number
        pull() |>
        first()
    }
  })

@@

```{r reactive_plots, include=FALSE}
# Beginning of the second reactive chunk =======================================
# It's necessary to split the observers into separate parts, with all necessary
# code duplicated, because of R's limitations.

@@

    # Testing and creating data frame
    html_test_create(
      input$html$datapath,
      as.character(input$start), as.character(input$end)
    )
  })

@@

  ## Excel data test (also above)-----------------------------------------------
  # Reactive function to test for Excel data quality (basic)
  datatest <- reactive({
    # let me know if anyone has a better idea for testing
    if (mean(unlist(lapply(exceldata(), is.character))) != 0) {
      TRUE
    } else {
      FALSE
    }
  })
  # Let the magic/disaster happen (i.e. execute when the user clicks the button)
}) |> bindEvent(input$click)
```
